### 2016-01-26 project/paper/sections/data.tex
Update data.tex

First, we determine features of people that might influence their probability of winning a Nobel Prize. They are elaborated in Section~\ref{ssec:features}. Next, we research whether and where this information can be found. The main data source are knowledge bases, also known as Linked Open Data in the Semantic Web. We can use SPARQL queries on an endpoint to easily retrieve structured data \cite{wc3SPARQL}. The used knowledge bases are discussed in Section~\ref{ssec:knowledgebases}. Needed information that is not (yet) linked has to be scraped from websites. These are discussed in Section~\ref{ssec:additional}. We use Perl scripts and regular expressions to extract the data from plain HTML text. All the retrieved data and all the used scripts can be found at the webpage for this paper: \url{kaw.wardschodts.ws}.

@@

>>>>

First, we determine features of people that might influence their probability of winning a Nobel Prize. They are elaborated in Section~\ref{ssec:features}.
Then, we decide what our training dataset and research dataset should look like in Section 2.2. Next, we research whether and where this information can be found. The main data source are knowledge bases, also known as Linked Open Data in the Semantic Web. We can use SPARQL queries on an endpoint to easily retrieve structured data \cite{wc3SPARQL}. The used knowledge bases are discussed in Section~\ref{ssec:knowledgebases}. Needed information that is not (yet) linked has to be scraped from websites. These are discussed in Section~\ref{ssec:additional}. We use Perl scripts and regular expressions to extract the data from plain HTML text. All the retrieved data and all the used scripts can be found at the webpage for this paper: \url{kaw.wardschodts.ws}.

@@

\subsection{Training dataset and research dataset}
The positive examples in our training dataset are of course the Nobel Prize winners. For the negative examples, we want to take people that were able to win a Nobel Prize but did not. Our chosen feature for work productivity does not make much sense for other categories then scientists and economists. As we want to learn from consistent data, we take scientists and economists born after 1850 as our negative examples.
The research dataset contains the politicians for which we want to answer the research question. Since the purpose of this project was to use the Semantic Web to answer a research question involving the Talk of Europa database, the research dataset consists of European politicians from this database.
